\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-07 paper.tex

\author{Michael Laskey,Zoe McCarthy, Sachin Patil, Pieter Abbeel and Ken Goldberg}% <-this % stops a space

@@

@@

\subsection{Our Extension}
From our distributions $p(c_i=\gamma(t))$ and $p(n_i = x)$, we can denote the variance on the following terms as $\sigma_{c_i}$ and $\Sigma_{n_i}$.
Thus,

>>>>

\author{Michael Laskey*,Zoe McCarthy*, Sachin Patil, Pieter Abbeel and Ken Goldberg}% <-this % stops a space

@@

\begin{theorem}
\label{lemma35}
For $w \in \mathbb{R}^3$, we have, for $n \in \mathbb{S}^2$ and for friction coefficient $\mu > 0$,

\begin{align}
\mbox{sup}_{x \in C(n)} <x,w> = <n,w> + \mu||n \times w||
\end{align}

Hence, for $u = (a,b) \in \mathbb{R}^3 \times \mathbb{R}^3 = \mathbb{R}^6$, we have

\begin{align}
h_{W_i(g)}(a,b) = <n_i,a+b\times(c_i-z)>+\mu ||n_i \times (a+b\times(c_i-z))||
\end{align}

\end{theorem}

@@

\subsection{Our Extension}
Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|<n_i,a+b\times (c_i-z)> - <n_i',a+b\times(c_i'-z')>|+\mu|||n_i \times (a+b \times (c_i -z)|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}. By using the following simple facts $||a|| \leq 1$, $||b|| \leq 1$,
